### 2019-02-04 introduction.tex
fixes on LTI and 2 std on LTI AROT plots

\fxnote{equipment specifications in the tower that might influence the WTC separtarion decision-talk to Haraldur!}

@@

Figure~\ref{fig:AROT_LTI_rwy19_H_M} may be used to illustrate the hypothesis. The current ICAO time reference separation, indicated by the red vertical line for BIKF RWY-19 will be relocated to the left for some of the aircraft pairs under the RECAT-EU scheme. This relocation will be more noticeable for C-C and C-D pairs formed from the ICAO H-M pairs, in which case the separation is reduced from 5 NM to 3 NM. A shift of the reference separation line creates the potential for a shift in the distribution of the LTI, as long as it does not overlap with the AROT. Furthermore, study on the runway capacity of significantly larger airports~\cite{kolos2013influence} suggests that the frequency distribution of LTI tends to compress or squeeze to the right of the reference line with less standard deviation about the mean when the air traffic is intensified.

>>>>

@@

Figure~\ref{fig:AROT_LTI_rwy19_H_M} may be used to illustrate the hypothesis. The current ICAO time reference separation, indicated by the red vertical line for BIKF RWY-19 will be relocated to the left for some of the aircraft pairs under the RECAT-EU scheme, following a decreased wake separation requirement. This relocation will be more noticeable for C-C and C-D pairs formed from the ICAO H-M pairs, in which case the separation is reduced from 5 NM to 3 NM. A shift of the reference separation line creates the potential for a shift in the distribution of the LTI, as long as it does not overlap with the AROT. Furthermore, study on the runway capacity of significantly larger airports~\cite{kolos2013influence} suggests that the frequency distribution of LTI tends to compress or squeeze to the right of the reference line with less standard deviation about the mean when the air traffic is intensified.
